output:
  #bookdown::html_document2: default
  #bookdown::word_document2: default
  bookdown::pdf_document2: 
    template: templates/template.tex
documentclass: book
#bibliography: [bibliography/references.bib, bibliography/additional-references.bib]
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:darwin-quote)'}
There is grandeur in this view of life, with its several powers, having been originally breathed into a few forms or into one; and that, whilst this planet has gone cycling on according to the fixed law of gravity, from so simple a beginning endless forms most beautiful and most wonderful have been, and are being, evolved.
```
(ref:darwin-quote) --- Charles Darwin [@Darwin1859]
<!-- note that the quote author won't show up when you knit just a single chapter -->
  

# (Additional Analyses) Training Events {#cites-and-refs}

\chaptermark{Citations and cross-refs}
\minitoc <!-- this will include a mini table of contents-->


## CEPEH Training Event C1


The CEPEH training event C1 held at the premises of University of Nottingham aiming to prepare participants for the practical elements of co-creation and implementation of chatbots as an educational resource. It combined both theoretical and hands-on training.
15 participants were from RISE, AUTH, UoN.

Project managers of partners signposted the person involved, and relevant announcements were made though social media channels to the wider public. External to the project speakers were from University of Leeds, and Computer Science Department of University of Nottingham. It included academics, medical doctors, and researchers with focus both on clinical research and digital innovations in healthcare education and IT specialist/learning technologists 11.18 years of experiences (SD=7.2). A balance between male and female participants achieved.



Participants were asked to highlight what they liked for each day and how each day can be improved. Findings are described below per day of the training event


Day 1  
The participants comment that they liked the design method for educational resources presented using a co-creation approach, they liked the interactions with other groups, and they liked the overview of existing chatbot resources of the partners. On the areas that can be improved, more media material were requested.


Day 2
Participants enjoyed the presentation from the invited speaker from another faculty of the University of Nottingham, the CEPEH recources presented and the storyboarding process. Participants highlighted that the participation of more clinicians in the event would be an added value in regards with the storyboarding process.


Day3
Participants liked the hands-on activities of the day also enjoyed the creativity of the groups on the online chatbot development tool. As an area of improvement, participants wanted more time on hands on sections.



```{r map Importing Data, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
try(museum <- read_excel("C:/Users/MattP/Desktop/Full DATA CEPEH Moh.xlsx"))
museum %>%
leaflet() %>%
addProviderTiles(providers$Esri.WorldImagery, group = "World Imagery") %>%
addProviderTiles(providers$Stamen.TonerLite, group = "Toner Lite") %>%
addLayersControl(baseGroups = c("Toner Lite", "World Imagery")) %>%
addMarkers(label = museum$museum,
           clusterOptions = markerClusterOptions(),
           popup = ifelse(museum$`Presidential Library`=="Yes",
                          "1 person around this area",
                          "1 person around this area")) %>% setView(lat = 53.921236496, lng = -1.1392187894608434, zoom = 09)
```


```{r MOHAMMED please make FREQ bar chart of top 15 Cities- sorted, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

city <- subset(data, select = "City")
city <- na.omit(city)

#table filter- to remove text from a coolumn:- !grep and then the cell text 

city <- subset(city, select = "City") %>%filter(!grepl('INVALID IPV4 ADDRESS', City))
city1 <- subset(city, select = "City") %>%filter(!grepl(' ', City))
view(city1)
colnames(city1)[1] = "City"

####insert table for frequency top 15 here

```


## CEPEH Training Event 2

**Pre-Training Event survey May 9th-13th 2022 Thessaloniki, Greece**

Twenty-six participants attended the Training Event, along with approximately 10 staff members. There were 21 undergraduate students and 5 postgraduate students, who completed the survey for a total of 26 responses. There were 86% of participants who stated they had not been to a similar event like the training event CEPEH facilitated. There were 90% of students who found the event schedule very organised, and 70% agreed most of the planned sessions were relevant to that interest with the remaining 30% not having enough experience to understand the context to determine if they are interested in the training event. There were 95% of students agreeing or strongly agreeing the training event location is great, the remaining person did not leave additional comments. 


Table 1 suggested attendees had minimal intention to share their own ideas due to lack of previous experience of attending such events, or due to lack of knowledge on the area. However, most were interested in listening to other groups and hearing contextual cases in healthcare.



There were 77% of participants stated they were novices in experience with chatbots in healthcare and were attending to learn more.  The remaining 23% (7 students) stated they were competent and had limited experience with chatbots in healthcare.


One day had several events regarding cybersecurity in healthcare. When asked before these events, 83% stated they were neutral or disagreed that they felt confident about their cybersecurity knowledge in healthcare. In addition, 80% stated they when neutral or disagreed that they felt they had strong cybersecurity safety in healthcare.  Table 2 shows the main pre and post results suggesting a positive experience for more than 75% of attendees on all measures. 



There were 90% (23) of students who heard about the event through a lecturer or a professor, the CEPEH newsletter (2), and 1 person was informed through the anatomy tutoring system at Karolinska Institute. Additionally, 60% suggested the training event to somebody else before the course started.


There were six individuals who stated neutral or disagree when asked if having issues on registration or finding the information for the event. This may have been due to being dependent on emails to receive the information, instead of a dedicated website where the information is available anytime. 


As this was face-to-face, participants were asked about sufficient Covid-19 precautions in place at the facility, 94% agreed with sufficient precautions, two individuals stated no but did not give further information in the additional input box provided.
In summary, most participants were undergraduate students with novice experience, happy with the training event location, felt the sessions were relevant to them, and most shared the event with their colleagues. The values of co-creation, chatbots in healthcare, and taking patient history were bestowed to students in an engaging and well-received manner. Notably, the highest ratings were for staff friendliness which is key to engagement and consistent interaction throughout the intense and long 5-day duration. The sessions were recorded there for the online recordings may be viewed with higher numbers over the subsequent weeks. 



